---
title: "Reproducible Research"
author: "Aleksandr Yakovlev"
date: "17 12 2019"
output: md_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Reproducible reserch


```{r head}
library(ggplot2)
data <- read.csv("activity.csv", header = TRUE, sep = ",", na.strings = "NA")
#data$date <- as.POSIXct(data$date)
head(data)
```
### Suumary data
```{r summary}
summary(data)
```
### Structure
```{r str}
str(data)
```
What is mean total number of steps taken per day?
For this part of the assignment, we can ignore the missing values in the dataset.
```{r total}
cleardata <- data[!is.na(as.character(data$steps)),]
```

1. Calculate the total number of steps taken per day
```{r perday}
steps_day <- aggregate(steps ~ date, data = cleardata, sum)
head(steps_day)
```

2. Make a histogram of the total number of steps taken each day
```{r hist}
hist(steps_day$steps, breaks = 25)
```





3. Calculate and report the mean and median of the total number of steps taken per day
```{r mean}
mean(steps_day$steps)
median(steps_day$steps)
```

What is the average daily activity pattern?
Make a time series plot (i.e. \color{red}{\verb|type = "l"|}type="l") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)
Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?
```{r }
steps_interval <- aggregate(cleardata$steps, by=list(interval=cleardata$interval), FUN=mean)
ggplot(steps_interval, aes(x = interval, y = x)) + geom_line(color="blue", size=1) + labs(title = "Avg. Daily Steps", x = "Interval", y = "Avg. Steps per day")

```

Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?
``` {r}

max(steps_interval$x)

```
## Imputing missing values
1. Missing value
```{r}
sum(is.na(as.character(data$steps)))
```

## Imputing missing values
1. Missing value
```{r}
newdata <- data
newdata$steps[is.na(data$steps)] <- mean(data$steps, na.rm = T)
colSums(is.na(newdata))

newsteps_day <- aggregate(steps ~ date, data = newdata, sum)
hist(newsteps_day$steps, breaks = 25)
#head(newdata)

```

#Panel plot comparing the average number of steps taken per 5-minute interval across weekdays and weekends

```{r}
newdata$DayType <-  ifelse(as.POSIXlt(newdata$date)$wday %in% c(0,6), 'weekend', 'weekday')
head(newdata)
newdata_mean <- aggregate(steps ~ interval + DayType, data=newdata, mean)
ggplot(newdata_mean, aes(interval, steps)) + 
    geom_line() + 
    facet_grid(DayType ~ .) +
    xlab("5-min intervals") + 
    ylab("avarage number of steps")


```


